### 2021-09-14 sections/healthcare_application/main.tex
Add small paragraph of news articles

>>>>

There are numerous new articles that focus on the problems that arise when 
ambulances stay parked outside of the hospital for a long amount of time
\cite{dailyrecords}, \cite{staffordshirelive}.
Some news reports also comment on the long idle time of ambulances when 
they are not in use \cite{herefordtimes} and there are several reports of 
examples where this became an issue for new patients \cite{southwalesargus}.
